Uncovering Distributed System Bugs\\ during Testing (not Production!)

### 2015-08-18 overview.tex
updates in overview

Example of liveness bug in Azure Storage vNext.

Liveness properties are much harder to specify and check since they apply over entire program executions and not just individual program states. Normally, liveness checking requires the identification of an infinite fair execution that never satisfies the liveness property~\cite{schuppan2004efficient, musuvathi2008fair}. Prior work~\cite{schuppan2004efficient} has proposed that assuming a program with finite state space, a liveness property can be converted into a safety property. Other researchers proposed the use of heuristics and exploring finite executions of an infinite state space system using random walks to identify if a liveness property is satisfied~\cite{killian2007life}.

>>>>

Liveness properties are much harder to specify and check since they apply over entire program executions and not just individual program states. The liveness property that is being checked in the Azure Storage vNext system is that a user-defined $N$ number of extent nodes must be always eventually available with the latest extent.

Normally, liveness checking requires the identification of an infinite fair execution that never satisfies the liveness property~\cite{schuppan2004efficient, musuvathi2008fair}. Prior work~\cite{schuppan2004efficient} has proposed that assuming a program with finite state space, a liveness property can be converted into a safety property. Other researchers proposed the use of heuristics and only exploring finite executions of an infinite state space system using random walks to identify if a liveness property is violated~\cite{killian2007life}.

TODO: Quickly say how we found Cheng's bug?

\subsection{Distributed systems testing today}
\label{sec:overview:testing}
